---
title: "Workshop"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Load the janitor package:

library(tidyverse)
library(janitor)
```

# Shortcut to make a R chunk:
Mac: control + option + i
Windows: ctrl + alt + i

# Shortcut to run a R chunk:
Mac: command + shift + return
Windows: ctrl + shift + enter

# Shortcut to run a R line:
Mac: command + return
Windows: ctrl + enter

# Shortcut to write %>%
Mac: command + shift + m
Windows: ctrl + shift + m


# Step 1: Read cap_data.csv into R

```{r}

cap_data <- read_csv("raw-data/cap_data.csv")

```

# Step 2: Take a look at the data using glimpse() and view()

# Step 3: Clean the data so it can be graphed with the number of complaints on
# the y-axis, year on the x-axis, and grouped by race

```{r}

cap_data_cleaned <- cap_data %>%
  group_by(year, race) %>% 
  count()

```

# Step 4: Look at the new cleaned data to see if it is what you want

# Step 5: Make the graph and then run the chunk to see it!

```{r}

cap_data_cleaned %>% 
  ggplot(aes(x = year, y = n, fill = reorder(race, -n))) +
  geom_col(position = "dodge") +
  theme_classic() +
  labs(title = "Number of Complaints Made Against Philly Police by Race",
       subtitle = "from May 2015 to April 2020",
       x = "",
       y = "",
       fill = "Race",
       caption = "Source: City of Philadelphia via OpenDataPhilly")

```

# Step 6: Training wheels off.

Say we want to just see the number of complaints made by Black and White Americans 
from 2016-2019. Filter the cap_data to meet this criteria and then clean it so it
can be used in a ggplot.

```{r}

cap_data_new <- cap_data %>% 
  filter(year %in% c(2016, 2017, 2018, 2019),
         race %in% c("Black", "White"))

```

```{r}

cap_data_new_cleaned <- cap_data_new %>% 
  group_by(year, race) %>% 
  count()

```

```{r}

cap_data_new_cleaned %>% 
  ggplot(aes(x = year, y = n, fill = reorder(race, -n))) +
  geom_col(position = "dodge") +
  theme_classic() +
  labs(title = "Number of Complaints Made Against Philly Police by Race",
       subtitle = "from 2016 to 2019",
       x = "",
       y = "",
       fill = "Race",
       caption = "Source: City of Philadelphia via OpenDataPhilly")

```

